Case Study: scRNA-seq (Mouse data, Wilcoxon-ranksum method)

### 2018-04-18 datasets/scrnaseq/scrnaseq-mouse-wilcox.Rmd
Fix typos in Wilcox scrnaseq

Here we are interested in performing differential expression analyses to determine
which genes have different expression among the two biological groups in each comparison.
We also apply two different analysis methods: Wilcoxon-ranksum [@finak2015] and scDD [@korthauer2016]. 
In this vignette, we will explore the human dataset analysed with Wilcoxon-ranksum.

>>>>

Here we are interested in performing differential expression analyses to determine
which genes have different expression among the two biological groups in each comparison.
We also apply three different analysis methods: Wilcoxon-ranksum, MAST [@finak2015],
and scDD [@korthauer2016]. 
In this vignette, we will explore the mouse dataset analysed with Wilcoxon-ranksum.
